Ethnicity Sensitive Author Disambiguation Using Semi-supervised Learning

### 2016-06-30 paper/author_disambiguation.tex
fit to 15 pages without titlesec
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{cite}
\usepackage[hidelinks]{hyperref}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\usepackage{color}
\usepackage{microtype}
\usepackage[small,compact]{titlesec}

\setlength{\intextsep}{5pt plus 0pt minus 0pt}
%\def\baselinestretch{0.99}

\newcommand{\longpage}{\enlargethispage{1.5\baselineskip}}

@@

Building on more than 1 million crowdsourced
annotations that we publicly release, we propose a new automated disambiguation
solution exploiting
this data (i) to learn an accurate classifier for identifying coreferring
authors and (ii) to guide the clustering of scientific publications by distinct
authors in a semi-supervised way. To the best of our knowledge, our analysis is
the first to be carried out on data of this size and coverage. With respect to
the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing new phonetic-based blocking strategies,
thereby increasing recall; (ii) adding strong ethnicity-sensitive features for
learning a linkage function, thereby tailoring disambiguation to non-Western
author names whenever necessary; and (iii) showing the importance of balancing
negative and positive examples when learning the linkage function.

>>>>

\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{cite}
\usepackage[hidelinks]{hyperref}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\usepackage{color}
\usepackage{microtype}

\setlength{\intextsep}{5pt plus 0pt minus 0pt}
\def\baselinestretch{0.99}

\newcommand{\longpage}{\enlargethispage{1.4\baselineskip}}

@@

Building on more than one million crowdsourced
annotations that we publicly release, we propose a new automated disambiguation
solution exploiting
this data (i) to learn an accurate classifier for identifying coreferring
authors and (ii) to guide the clustering of scientific publications by distinct
authors in a semi-supervised way. To the best of our knowledge, our analysis is
the first to be carried out on data of this size and coverage. With respect to
the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing new phonetic-based blocking strategies,
thereby increasing recall; (ii) adding strong ethnicity-sensitive features for
learning a linkage function, thereby tailoring disambiguation to non-Western
author names whenever necessary; and (iii) showing the importance of balancing
negative and positive examples when learning the linkage function.
